### 2015-02-02 CV/cv.tex
Minor CV update to ordering
Updated CV for journal acceptance

    6195 Gossard                            \hfill phone: (314) 313-1281          \vspace{0mm}\\\vspace{0mm}%
    East Lansing, Michigan, 48823                          \hfill email: brianwgoldman@acm.org          %\vspace{0mm}%\\\vspace{0mm}%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Optimization, Artificial Intelligence, Evolutionary Computation, Machine Learning

@@

    \begin{enumerate}
    \item
    B. W. Goldman and W. F. Punch,
    ``Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid,''
    \textbf{Invited Paper}, \textsl{Evolutionary Computation Journal} (Impact Factor 3.733), In Review

@@

    \item
    B. W. Goldman and W. F. Punch,
    ``Parameter-less Population Pyramid,''
    \textsl{GECCO} (Acceptance Rate 33\%), pp. 785--792, 2014
    \textbf{Won Best Paper in Track}

>>>>

    6195 Gossard                            \hfill phone: (314) 313-1281          \vspace{0mm}\\\vspace{0mm}%
    East Lansing, Michigan, 48823                          \hfill email: brianwgoldman@acm.org          %\vspace{0mm}%\\\vspace{0mm}%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Optimization, Machine Learning, Artificial Intelligence, Evolutionary Computation

@@

    \begin{enumerate}
    \item
    B. W. Goldman and W. F. Punch,
    ``Fast and Efficient Black Box Optimization using the Parameter-less Population Pyramid,''
    \textbf{Invited Paper}, \textsl{Evolutionary Computation Journal} (Impact Factor 3.733), Accepted With Revisions

@@

    \item
    B. W. Goldman and W. F. Punch,
    ``Parameter-less Population Pyramid,''
    \textsl{GECCO} (Acceptance Rate 33\%), pp. 785--792, 2014
    \textbf{Best paper award winner}
